Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems and their personnel. Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is more rarely activitated in France, and only on an voluntary individual teacher's basis. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

>>>>

So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems and their personnel. Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, but it is much more rarely activitated in France, and only on an voluntary individual teacher's basis. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
